Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-12 write-ups/PLDI/paper.tex
Add paragraph on the GPU we tested

@@

@@

\ADComment{Tyler and Hugues, please write.}

>>>>

\HEComment{This is more or less already done in section
\ref{sec:programmingguidelines} , maybe no need to rewrite here?}

@@

\HEComment{the reason we need SVM fine grain and atomics may be better
discussed directly in the section on implementation?}

Our implementation approach requires two optional features of OpenCL
$2.0$, namely SVM fine-grained buffers and SVM atomics, which are
currently not widely supported. \nvidia chips are ruled out since
\nvidia does not support OpenCL $2.0$. AMD support SVM atomics only
their Kaveri family of chips and only on Linux, requiring to compile the
latest driver.  \HEComment{do we need to mention the struggle for AMD ?}
Among the GPUs available to us, only 4 support our requirements: Intel
HD 520, HD 5500 and IRIS 6100, and AMD Radeon R7.

@@
